FinalManuscript_DISCS_UG

### 2018-10-08 parts/02_relatedliterature_05partiallyhomomorphic.tex
final final final
final final final

\subsection{General Exponentiation Protocol for Paillier and DGK}
\label{ssec:exponentiationprotocol}
In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms.

@@

This can be extended to arbitrary integer powers.
Suppose Alice encrypts and integer $x$, and Bob has $E(x), E(x^2), ..., E(x^{n-1})$ and wants to obtain $E(x^n)$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice sends $E((x+r)^n)$ to Bob.
	\item Bob then computes
	\begin{align*}
		E((x+r)^n) - E\left(\sum_{i=1}^{n-1}{\binom{n}{i}x^ir^{n-i}}\right),
	\end{align*}
	which evaluates to $E(x^n)$ by the binomial theorem.
\end{itemize}

>>>>

\subsection{Secure Exponentiation and Multiplication Protocols}
\label{ssec:exponentiationprotocol}
In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.

@@

We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
\begin{itemize}
	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E((x+y)^2)$ to Bob.
	\item Bob then computes
	\begin{align*}
		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
		&= E(2xy)
	\end{align*}
	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$. Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
\end{itemize}
